Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-04-22 paper.tex
fixing streaming terms and some notation

The transport of relativistic electrons and protons across cosmic time
into galaxy clusters is a complex problem that depends on the velocity
field of the gas (and its thermodynamic properties such as density,
temperature, and pressure) as well as non-thermal processes
(turbulence, magnetic fields, fossil CRs). We use high resolution
galaxy cluster simulations to derive the thermal and fossil CR
properties (shock accelerated primary CRes and CRps, as well as
secondary CRes produced in p-p collisions)
\citep{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}.

@@

\subsection{Cosmic ray transport}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations; because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes to only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaneously produces flat CRp profiles. \sout{We assume that CRs cannot
stream significantly past perpendicular $B$-fields at the accretion
shock, so that the total number of CRs is conserved within the galaxy
cluster during the streaming process.}

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
- \bnabla\bcdot \vec{F}_\rmn{stream}
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (r) and Coulomb (coul) losses,
$D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
adiabatic gains and losses and the $\bnabla\bcdot
\vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
streaming. For details about $F_\rmn{stream}$ please see
\citet{wiener13}. During post-processing of our Coma-like cluster
simulation, we solve the Fokker-Planck equation over a redshift
interval from $z=5$ to 0. The simulated cluster undergoes a major
merger over the last 1-2~Gyrs that is thought to inject large
turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
  also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
about one Gyr after core passage the fields have decayed down to the
smallest scales where reacceleration is most efficient ($D_{pp}\sim
k_\rmn{cut}$) and the radio halo turns on shortly after. Note that the
exact decay time of the turbulens is of minor importance, since the
thermal and CR quantities are very similar a few 100 Myrs before and
after $z=0$ where we have chosen to evaluate the simulations. This
delay naturally explains why giant radio halos are only seen in a
fraction of all merging clusters. In all our calculations we assume
that turbulent reacceleration efficiently accelerates particles for
$\tau_\rmn{cl}\sim650$~Myrs (which is roughly the cascade time on which
turbulence is damped) and that during this turbulent phase CR
streaming and spatial diffusion can be neglected. In our \Mstream
model, CR streaming and diffusion are incorporated separately during
kinematically quiescent times that precede the merger. As a result,
flat CRp profiles are produced on relatively short timescales ($\sim
0.1-0.5$ Gyr). This allows us to implicitly solve for CR streaming in
our calculations, where we adopt a toy model that enforce a flat CRp
profile at all quiescent times \citep{wiener13}. We assume that CRs
cannot stream significantly past perpendicular $B$-fields at the
accretion shock, so that the total number of CRs is conserved within
the virial radius during the streaming process. Finally, since
streaming is much more efficient for the CRps, we can ignore this
effect for the CRes.

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
{{d f_{\rmn{p}}(p,t)}\over{d t}} &=&
{{\partial }\over{\partial p}}
\left\{
f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm C}
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)\right.\right.
\nonumber\\
&-&\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{p}}(p,t)
- \bnabla\bcdot \vec{F}_\rmn{stream}
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock
accelerated CRps as a function of momentum $p$ and time $t$, and
$\tau_{\rm had}$ is the timescale of hadronic losses that produce
pions via CRp collisions with thermal protons of the ICM
\cite[e.g.][]{brunetti11}.

@@

During reacceleration the CRps approximately gain a factor 
\begin{equation}
  \label{eq:Creacc}
  \Delta C_\rmn{reacc.} \sim
  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
\end{equation}
if injection and cooling are neglected. The reaccelerated CRs are then
exponentially dependent on $tau_D\sim 1/D_\rmn{pp}$ as long as $\tau_D
\lesssim \tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration
of reacceleration of the merger which we assume to be 650~Myrs long.

@@

We adopt both the density \cite{1992A&A...259L..31B} and temperature
\cite{2009ApJ...696.1886B,2001A&A...365L..67A} profiles derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/294\,\rmn{kpc}\right)^2\right]^{1.125}}\nonumber\\
T k_B &=& 8.25\,\rmn{keV} \left[1+\left(R/0.5R_{200}\right)^2\right]^{-0.32}\,.
\end{eqnarray}
The virial radius of Coma is given by $R_{200} = 2300\,\rmn{kpc}$.
The bulk of the CRps are injected by relatively low Mach number shocks
and parameterized by $f_\rmn{CRp,inj}(p) =
C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
where the normalization is fixed by assuming that the injected CR
energy in the last 650~Myrs make up 0.03\% of the thermal energy
inside the virial radius, i.e.
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V = 0.0003$. The spectrum of
  the initial CRp distribution is determined by the steady state between
  injection and cooling,
\begin{equation}
 f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
\rmn{d}p'}{\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where the normalization is fixed by
$\int_0^{R_{200}}\epsilon_\rmn{CRp,0}
\rmn{d}V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V =
0.003$. Similarly, the initial CRe distribution is given by the steady
state between cooling (Coulomb, inverse Compton, and synchrotron) and
injection of secondary CRes from $f_{CRp,0}$. We also include the
continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reaccelerating both the CRps
and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_e
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

@@

We use a simple test-particle model for the CR acceleration and
injection, where each shock inject CRs that trace a power-law in
momentum,
\begin{equation}
  f(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,
\end{equation}
determined by the normalization $C(t)$ and the spectral index
$\alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}{(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}$
that depends on the adiabatic index $\gamma_\rmn{ad} = 5/3$ and the
Mach number of the shock $\mathcal{M}$. It is given by the ratio of
the upstream velocity ($u_2$) and the sound speed ($c_s$). The CR
number density and CR energy density are derived from $n_\rmn{CR} =
\int_{p_\rmn{inj}}^\infty \dd p\, f(p)$ and $\epsilon_\rmn{CR} =
\int_{p_\rmn{inj}}^\infty \dd p\, f(p) \,T(p)$, respectively, where
$T(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
particle with momentum $p$. We adopt a fit to Monte Carlo
simulations of the thermal leakage process that relates the momentum
of injected protons ($p_\rmn{inj}$) to the thermal energy
($p_\rmn{th}$) of the shocked plasma \citep{kang11}:
\begin{eqnarray}
  \label{eq:qinj}
  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,k T_2}{m c^2}}\,, \nonumber \\
  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn th}\,c} \left(1+
  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
\end{eqnarray}
Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
shock normal. The physical range of $\eb$ is quite uncertain due to
complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
which we will later see corresponds to a conservative maximum energy
acceleration efficiency for protons of $10\%$. To derive the
acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
particle injection efficiency, which is the fraction of downstream
thermal gas particles which experience diffusive shock acceleration
\citep[for details see ][]{pinzke13},
\begin{equation}
  \label{eq:eta}
  \eta_\rmn{CR,lin} =
  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
  \rmn{e}^{-x_\rmn{inj}^2}.
\end{equation}
The particle injection efficiency is a strong function of
$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
energy density of CRs that are injected and accelerated at the shock
(neglecting the CR back reaction on the shock) is given by
\begin{equation}
\label{eq:CR_energy} 
  \Delta\epsilon_\rmn{CR,lin} =
  \eta_\rmn{CR,lin}(\mathcal{M})\,T_\rmn{CR}(\mathcal{M},p_\rmn{inj})\,n_\rmn{th}(T_2),
\end{equation}
and the CR energy injection and acceleration efficiency is:
\begin{equation}
  \zeta_\rmn{lin} =
  \frac{\Delta\epsilon_\rmn{CR,lin}}{\Delta\epsilon_\rmn{diss}},
   \quad\mbox{where}\quad
  \Delta\epsilon_\rmn{diss} = \epsilon_\rmn{th2} - \epsilon_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
\label{eqn:energy_frac}  
\end{equation}
The dissipated energy density in the downstream regime,
$\Delta\epsilon_\rmn{diss}$, is given by the difference of the thermal
energy densities in the pre- and post-shock regimes, corrected for the
adiabatic energy increase due to gas compression.

@@

In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
acceleration efficiency (see \cite{pinzke13} for more
discussion). However, as recent PIC simulations have shown, this is
likely very different at weak shocks, with electrons efficiently
accelerated at perpendicular shocks
\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
or smaller. Some observations of radio relics suggest high values of
$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
CRes as a viable alternative scenario to secondary CRes as seeds for
the giant RHs. In our {\em M-primaries} scenario, the injected
distribution of CRes is derived in the same way as for the CRps. Once
they have been accelerated to relativistic energies, injected
electrons and protons are indistinguishable. We therefore assume that
CRp and CRe have the same distribution function $f_\rmn{CRe}(p) =
K_\rmn{ep} f_\rmn{CRp}(p)$, with a different normalization (due to
differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
  viable for primarily perpendicular
  shocks][]{2014ApJ...794..153G}. While this appears to contradict the
radial bias of magnetic fields in the bulk of the ICM as suggested by
observations \citep{2010NatPh...6..520P} and cluster simulations
\citep{2011ApJ...740...81R}, it does not necessarily apply to the
accretion shock regions, which show a field geometry with a net
perpendicular bias with respect to the shock normal---at least for
giant radio relics \citep{2010Sci...330..347V}.

>>>>

The transport of relativistic electrons and protons across cosmic time
into galaxy clusters is a complex problem that depends on the velocity
field of the gas (and its thermodynamic properties such as density,
temperature, and pressure) as well as non-thermal processes
(turbulence, magnetic fields, fossil CRs). We use high resolution
galaxy cluster simulations to derive the thermal and fossil CR
properties \citep[shock accelerated primary CRes and CRps, as well as
  secondary CRes produced in p-p collisions,
  see][]{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}.

@@

\subsection{Cosmic ray transport}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations. Because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes to only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaneously produces flat CRp profiles. \sout{We assume that CRs cannot
stream significantly past perpendicular $B$-fields at the accretion
shock, so that the total number of CRs is conserved within the galaxy
cluster during the streaming process.}

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (r) and Coulomb (coul) losses,
$D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
adiabatic gains and losses.

During post-processing of our Coma-like cluster simulation, we solve
the Fokker-Planck equation over a redshift interval from $z=5$ to
0. The simulated cluster undergoes a major merger over the last
1-2~Gyrs that is thought to inject large turbulent eddies. Following
standard approaches
\citep{brunetti07,brunetti11,2004ApJ...614..757Y,2015ApJ...800...60M}
we assume that about one Gyr after core passage the fields have
decayed down to the smallest scales where reacceleration is most
efficient ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on
shortly after. Note that the exact decay time of the turbulens is of
minor importance, since the thermal and CR quantities are very similar
a few 100 Myrs before and after $z=0$ where we have chosen to evaluate
the simulations. This delay naturally explains why giant radio halos
are only seen in a fraction of all merging clusters. In all our
calculations we assume that turbulent reacceleration efficiently
accelerates particles for $\tau_\rmn{cl}\sim650$~Myrs (which is
roughly the cascade time on which turbulence is damped) and that
during this turbulent phase CR streaming and spatial diffusion can be
neglected. In our \Mstream model, CR streaming and diffusion are
incorporated separately during kinematically quiescent times that
precede the merger. As a result, flat CRp profiles are produced on
relatively short timescales ($\sim 0.1-0.5$ Gyr). This allows us to
implicitly solve for CR streaming in our calculations, where we adopt
a toy model that enforce a flat CRp profile at all quiescent times
\citep{wiener13}. We assume that CRs cannot stream significantly past
perpendicular $B$-fields at the accretion shock, so that the total
number of CRs is conserved within the virial radius during the
streaming process. Finally, since streaming is much more efficient for
the CRps, we can ignore this effect for the CRes.

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
\lefteqn{
  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
  {{\partial }\over{\partial p}}
  \left\{
  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm C}
    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
\nonumber\\
&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
\nonumber\\
&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
$Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
CRps as a function of momentum $p$ and time $t$, and $\tau_{\rm had}$
is the timescale of hadronic losses that produce pions via CRp
collisions with thermal protons of the ICM \cite[e.g.][]{brunetti11}.

@@

During reacceleration the CRps approximately gain a factor 
\begin{equation}
  \label{eq:Creacc}
  \Delta C_\rmn{reacc.} \sim
  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
\end{equation}
if injection and cooling are neglected. The reaccelerated CRs are then
exponentially dependent on $\tau_D\sim 1/D_\rmn{pp}$ as long as $\tau_D
\lesssim \tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration
of reacceleration of the merger which we assume to be 650~Myrs long.

@@

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,.
\end{eqnarray}
The virial and core radii of Coma are given by $R_{200} =
2300\,\rmn{kpc}$ and $R_{\rmn{c}} = 294\,\rmn{kpc}$, respectively.
The bulk of the CRps are injected by relatively low Mach number shocks
and parameterized by $f_\rmn{CRp,inj}(p) =
C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
where the normalization is fixed by assuming that the injected CR
energy in the last 650~Myrs make up 0.03\% of the thermal energy
inside the virial radius, i.e.
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalization by requiring
$\int_0^{R_{200}}\epsilon_\rmn{CRp,0}
\rmn{d}V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
0.003$. Similarly, the initial CRe distribution is given by the steady
state between cooling (Coulomb, inverse Compton, and synchrotron) and
injection of secondary CRes from $f_{CRp,0}$. We also include the
continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reaccelerating both the CRps
and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_e
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

@@

We use a simple test-particle model for the CR acceleration and
injection, where each shock inject CRs that trace a power-law in
momentum,
\begin{equation}
  f(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
\end{equation}
determined by the normalization $C(t)$ and the spectral index
$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
$\mathcal{M}$. It is given by the ratio of the upstream velocity
($u_2$) and the sound speed ($c_s$). The CR number density and CR
energy density are derived from $n_\rmn{CR} =
\int_{p_\rmn{inj}}^\infty \dd p\, f(p)$ and $\epsilon_\rmn{CR} =
\int_{p_\rmn{inj}}^\infty \dd p\, f(p) \,T(p)$, respectively, where
$T(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
particle with momentum $p$. We adopt a fit to Monte Carlo simulations
of the thermal leakage process that relates the momentum of injected
protons ($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the
shocked plasma \citep{kang11}:
\begin{eqnarray}
  \label{eq:qinj}
  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,k T_2}{m c^2}}\,, \nonumber \\
  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn th}\,c} \left(1+
  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
\end{eqnarray}
Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
shock normal. The physical range of $\eb$ is quite uncertain due to
complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
which we will later see corresponds to a conservative maximum energy
acceleration efficiency for protons of $10\%$. To derive the
acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
particle injection efficiency, which is the fraction of downstream
thermal gas particles which experience diffusive shock acceleration
\citep[for details see ][]{pinzke13},
\begin{equation}
  \label{eq:eta}
  \eta_\rmn{CR,lin} =
  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
  \rmn{e}^{-x_\rmn{inj}^2}.
\end{equation}
The particle injection efficiency is a strong function of
$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
energy density of CRs that are injected and accelerated at the shock
(neglecting the CR back reaction on the shock) is given by
\begin{equation}
\label{eq:CR_energy} 
  \Delta\epsilon_\rmn{CR,lin} =
  \eta_\rmn{CR,lin}(\mathcal{M})\,T_\rmn{CR}(\mathcal{M},p_\rmn{inj})\,n_\rmn{th}(T_2),
\end{equation}
and the CR energy injection and acceleration efficiency is:
\begin{equation}
  \zeta_\rmn{lin} =
  \frac{\Delta\epsilon_\rmn{CR,lin}}{\Delta\epsilon_\rmn{diss}},
   \quad\mbox{where}\quad
  \Delta\epsilon_\rmn{diss} = \epsilon_\rmn{th2} - \epsilon_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
\label{eqn:energy_frac}  
\end{equation}
The dissipated energy density in the downstream regime,
$\Delta\epsilon_\rmn{diss}$, is given by the difference of the thermal
energy densities in the pre- and post-shock regimes, corrected for the
adiabatic energy increase due to gas compression.

@@

In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
acceleration efficiency \citep[see][for more
  discussion]{pinzke13}. However, as recent PIC simulations have
shown, this is likely very different at weak shocks, with electrons
efficiently accelerated at perpendicular shocks
\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
or smaller. Some observations of radio relics suggest high values of
$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
CRes as a viable alternative scenario to secondary CRes as seeds for
the giant RHs. In our {\em M-primaries} scenario, the injected
distribution of CRes is derived in the same way as for the CRps. Once
they have been accelerated to relativistic energies, injected
electrons and protons are indistinguishable. We therefore assume that
CRp and CRe have the same distribution function $f_\rmn{CRe}(p) =
K_\rmn{ep} f_\rmn{CRp}(p)$, with a different normalization (due to
differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
  viable for primarily perpendicular
  shocks][]{2014ApJ...794..153G}. While this appears to contradict the
radial bias of magnetic fields in the bulk of the ICM as suggested by
observations \citep{2010NatPh...6..520P} and cluster simulations
\citep{2011ApJ...740...81R}, it does not necessarily apply to the
accretion shock regions, which show a field geometry with a net
perpendicular bias with respect to the shock normal---at least for
giant radio relics \citep{2010Sci...330..347V}.
